Signatures and Induction Principles for Higher Inductive-Inductive Types

### 2019-08-13 paper.tex
stuff

(5) There is a different equality type former, which can be used to express
paths between type constructors. To our knowledge, this has not been considered
in previous HIT literature, although Cartmell considered equations between sorts
in generalized algebraic theories \cite{gat}. For an example, paths between type
constructors allow a compact definition of integers:
\begin{alignat*}{5}
  & \boldsymbol{\cdot},\,\,Int : U,\,\,zero : \underline{Int},\,p : Int =_\U Int
\end{alignat*}
Here, successor and predecessor functions can be recovered from the $p : Int
=_\U Int$ equality, by transporting an $Int$ along $p$ or $p^{-1}$. This
signature could be unfolded to a larger one, by replacing $p : Int =_\U Int$
with an explicit $suc : Int \ra \underline{Int}$ constructor and additional
constructors expressing that $suc$ is an equivalence. The definition of $Int$
with a successor equivalence was previously suggested by Altenkirch and Pinyo
\cite{pinyo2018integers} and Cavallo and M\"ortberg \cite{cavallointegers}. Our
signature can be viewed as a shorthand for the unfolded version.

@@

>>>>

(5) There is a different equality type former, which can be used to express
paths between type constructors. To our knowledge, this has not been considered
in previous HIT literature, although Cartmell considered equations between sorts
in generalized algebraic theories \cite{gat}. For an example, paths between type
constructors allow a compact definition of integers:
\begin{alignat*}{5}
  & \boldsymbol{\cdot},\,\,Int : U,\,\,zero : \underline{Int},\,p : Int =_\U Int
\end{alignat*}
Here, successor and predecessor functions can be recovered from the $p : Int
=_\U Int$ equality, by transporting an $Int$ along $p$ or $p^{-1}$. This
signature could be unfolded to a larger one, by replacing $p : Int =_\U Int$
with an explicit $suc : Int \ra \underline{Int}$ constructor and additional
constructors expressing that $suc$ is an equivalence. The definition of $Int$
with a successor equivalence was previously suggested by Altenkirch and Pinyo
\cite{pinyo2018integers} and Cavallo and M\"ortberg \cite{cavallointegers}.

@@

In the presence of the univalence axiom, type constructor equations can be
always equivalently represented using usual path constructors, by adding
explicit equivalences to a signature. In this case, type constructor equations
serve as a shorthand for equivalences.
